### 2020-09-22 paper/coloringBergeGraphs.tex
Final pdf to check

\Cref{sec:InformationTheory} and \Cref{sec:computingTheta} are based on lecture notes by Lovász \cite{Lovasz95}.

@@

Suppose we have a noisy communication channel in which certain signal values can be confused with others. For instance, suppose our channel has five discrete signal values, represented as 0, 1, 2, 3, 4. However, each value of $i$ when sent across the channel can be confused with value $(i \pm 1)$ mod $5$. This situation can be modeled by a graph $C_5$ (\cref{fig:c5}) in which vertices correspond to signal values and two vertices are connected if and only if the values they represent can be confused.

@@

For $k = 1$, maximum number of messages we can send without confusion in a single step is equal to $\alpha(G)$. To describe longer messages we use \emph{strong product} $G \cdot H$ of two graphs $G = (V, E)$, $H = (W, F)$ as the graph with $V(G \cdot H) = V \times W$, with $(i, u)(j, v) \in E(G \cdot H)$ if and only if $ij \in E$ and $uv \in F$, or $ij \in E$ and $u = v$, or $i = j$ and $uv \in F$. Given channel modeled by $G$ it is easy to see that the maximum number of distinguishable words of length 2 is equal to $\alpha(G \cdot G)$, and in general the number of distinguishable words of length $k$ is equal to $\alpha(G^k)$ which gives us $\sqrt[k]{\alpha(G^k)}$ as the number of distinguishable signals per single transmission. So, we can define the Shannon capacity of the channel defined by $G$ as $\Theta(G) = \sup\limits_k \sqrt[k]{\alpha(G^k)}$.

@@

\begin{defn}[semidefinite program]
  Let $A_1, \ldots, A_n, B$ be given symmetric $m \times m$ matrices and be $c \in \mathbb{R}^n$ a given vector. A \emph{semidefinite program} is an optimization problem of the following form:
  \begin{equation*}
    \begin{array}{ll@{}ll}
      \text{minimize}   & c^\intercal x                          & \\
      \text{subject to} & x_1A_1 + \ldots + x_nA_n - B \succeq 0   \\
    \end{array}
  \end{equation*}
  Any choice of the values $x_i$ that satisfies the given constraint is called a \emph{feasible solution}.
\end{defn}

@@

\section{Classical algorithms}
\label{sec:classicalColoring}

@@

@@

The algorithm for coloring square-free Berge graphs is much more complex than CCLSV algorithm for Berge graphs recognition and would be much harder to implement. The main idea is that, if square-free Berge graph $G$ is not a member of class that is simple to recognize and color (Artemis graphs), then it must have an induced prism. We find it and grow it until it is maximal and then we can create a partition of $G$, that we color recursively. The paper in which the algorithm is presented \cite{coloringSquareFree} is of much more mathematical ''flavor'' than \cite{MC05} -- there is a proof that a $O(|V|^9)$ algorithm exists, but actually deducing it from the paper isn't straightforward. We provide its pseudocode in the Appendix A.

>>>>

\Cref{sec:InformationTheory,sec:computingTheta} are based on lecture notes by Lovász \cite{Lovasz95}.

@@

Suppose we have a noisy communication channel in which certain signal values can be confused with others. For instance, suppose our channel has five discrete signal values, represented as 0, 1, 2, 3, 4. However, each value of $i$ when sent across the channel can be confused with value $(i \pm 1)$ mod $5$. This situation can be modeled by a graph $C_5$ (\Cref{fig:c5}) in which vertices correspond to signal values and two vertices are connected if and only if the values they represent can be confused.

@@

For $k = 1$, maximum number of messages we can send without confusion in a single step is equal to the stability number $\alpha(G)$. To describe longer messages we use \emph{strong product} $G \cdot H$ of two graphs $G = (V, E)$, $H = (W, F)$ as the graph with $V(G \cdot H) = V \times W$, with $(i, u)(j, v) \in E(G \cdot H)$ if and only if $ij \in E$ and $uv \in F$, or $ij \in E$ and $u = v$, or $i = j$ and $uv \in F$. Given channel modeled by $G$ it is easy to see that the maximum number of distinguishable words of length 2 is equal to $\alpha(G \cdot G)$, and in general the number of distinguishable words of length $k$ is equal to $\alpha(G^k)$ which gives us $\sqrt[k]{\alpha(G^k)}$ as the number of distinguishable signals per single transmission. So, we can define the Shannon capacity of the channel defined by $G$ as $\Theta(G) = \sup\limits_k \sqrt[k]{\alpha(G^k)}$.

@@

\begin{defn}[semidefinite program]
  Let $A_1, \ldots, A_n, B$ be given symmetric $m \times m$ matrices and be $c \in \mathbb{R}^n$ be a given vector. A \emph{semidefinite program} is an optimization problem of the following form:
  \begin{equation*}
    \begin{array}{ll@{}ll}
      \text{minimize}   & c^\intercal x                          & \\
      \text{subject to} & x_1A_1 + \ldots + x_nA_n - B \succeq 0   \\
    \end{array}
  \end{equation*}
  Any choice of the values $x_i$ that satisfies the given constraint is called a \emph{feasible solution}.
\end{defn}

@@

\section{Combinatorial algorithms}
\label{sec:classicalColoring}

@@

\subsubsection{Coloring square-free Berge graphs}

@@

The algorithm for coloring square-free Berge graphs is much more complex than the CCLSV algorithm for Berge graphs recognition and would be much harder to implement.  
The main idea is that, if square-free Berge graph $G$ is not an Artemis graph, then it must have an induced prism. We find it and grow it into a structure called a hyperprism, which is a generalization of a prism. Then, we grow it further either to find a maximal induced hyperprism, or encounter an induced subgraph that is the line graph of a bipartite subdivision of $K_4$. If the latter outcome happens, we can grow it in turn into a rather complex structure called a $J$-strip system and then into a maximal $J$-strip system. When we have found a maximal induced hyperprism or a maximal $J$-strip system, we can find a partition of graph $G$ that we can color recursively.

The paper in which the algorithm is presented \cite{coloringSquareFree} is of much more mathematical ''flavor'' than \cite{MC05} -- there is a proof that a $O(|V|^9)$ algorithm exists, but actually deducing it from the paper isn't straightforward. We provide its pseudocode in the Appendix A. We believe that the work done there is a structurization of the algorithm that is a required step for a possible future work of implementing it.

### 2020-09-22 paper/definitions.tex
Final pdf to check

\begin{defn}[anticlique]
  An \emph{independent set} or an \emph{anticlique} is a graph of the form $G = (V, \emptyset)$, that is no vertices are connected.
\end{defn}
In a similar fashion, given a graph $G = (V, E)$, a subset of its vertices $V' \subseteq V$ will be called \emph{independent} (in the context of $G$) if and only if $G[V']$ is an anticlique.

>>>>

\begin{defn}[independent set]
  An \emph{independent set} or a \emph{stable set} is a graph of the form $G = (V, \emptyset)$, that is no vertices are connected.
\end{defn}
In a similar fashion, given a graph $G = (V, E)$, a subset of its vertices $V' \subseteq V$ will be called \emph{independent} (in the context of $G$) if and only if $G[V']$ is an independent set.

### 2020-09-22 paper/main.tex
Fixes
Final pdf to check

\begin{abstract}
	Perfect graphs are a subject of intense study since their introduction in 1961. Only in 2001 the famous Perfect graph conjecture was proven to be true and in 2005 a polynomial method of determining if a graph is perfect was found. Since 1988 an algorithm is known for coloring perfect graphs, but it uses an ellipsoid method which is said to be complicated and impractical. As recently as in 2018 a polynomial algorithm for coloring perfect graphs without squares was published, that uses a combinatorial approach.

@@

\listoftheorems[ignoreall,show={defn}]
\renewcommand{\listtheoremname}{List of algorithms}
\listoftheorems[ignoreall,show={alg}]
\tableofcontents

>>>>

\begin{abstract}
	Perfect graphs are a subject of intense study since their introduction in 1961. Only in 2001 the famous perfect graph conjecture was proven to be true and in 2005 a polynomial method of determining if a graph is perfect was found. Since 1988 an algorithm is known for coloring perfect graphs, but it uses an ellipsoid method which is said to be complicated and impractical. As recently as in 2018 a polynomial algorithm that uses a combinatorial approach for coloring perfect graphs without squares was published.

@@

\listoftheorems[ignoreall,show={defn}]
\renewcommand{\listtheoremname}{List of algorithms}
\makeatletter
\renewcommand\thmt@listnumwidth{2.6em}
\makeatother
\listoftheorems[ignoreall,show={alg}]
\tableofcontents

### 2020-09-22 paper/perfectGraphs.tex
Final pdf to check

The first step to solve the problem of recognizing perfect graphs was the \emph{(weak) perfect graph theorem} first conjured by Berge in 1961~\cite{CB61} and then proven by Lovász in 1972~\cite{LL72}.

@@

In 1961 Berge conjured that a graph is perfect if and only if it contains no odd holes and no odd antiholes in what has become known as a strong perfect graph conjecture. In 2001 Chudnovsky et al. have proven it and published the proof in an over 150 pages long paper \citetitle{MC06} \cite{MC06}.

>>>>

The first step to solve the problem of recognizing perfect graphs was the \emph{(weak) perfect graph theorem} first conjectured by Berge in 1961~\cite{CB61} and then proven by Lovász in 1972~\cite{LL72}.

@@

In 1961 Berge conjectured that a graph is perfect if and only if it contains no odd holes and no odd antiholes in what has become known as a strong perfect graph conjecture. In 2001 Chudnovsky et al. have proven it and published the proof in an over 150 pages long paper \citetitle{MC06} \cite{MC06}.
